quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-13 paper-quollr.Rmd
Added hexgonal grid

### $2\text{-}D$ model visualization

The `geom_hexgrid()` function is used to plot the hexagonal grid from the provided centroid data set.

@@

>>>>

### Hexagonal grid

The `geom_hexgrid()` function introduces a custom `ggplot2` layer designed for visualizing hexagonal grid on a provided set of bin centroids.

To display the complete grid, users should supply all available bin centroids.

@@

If the goal is to plot only the subset of hexagons that correspond to bins containing data points, then only the centroids associated with those bins should be passed.

ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
```

### Triangular mesh

### 2025-05-13 paper-quollr.tex
Added hexgonal grid

\subsubsection{\texorpdfstring{\(2\text{-}D\) model visualization}{2\textbackslash text\{-\}D model visualization}}\label{text-d-model-visualization}

The \texttt{geom\_hexgrid()} function is used to plot the hexagonal grid from the provided centroid data set.

@@

@@

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-30-1}

>>>>

\subsubsection{Hexagonal grid}\label{hexagonal-grid}

The \texttt{geom\_hexgrid()} function introduces a custom \texttt{ggplot2} layer designed for visualizing hexagonal grid on a provided set of bin centroids.

To display the complete grid, users should supply all available bin centroids.

@@

If the goal is to plot only the subset of hexagons that correspond to bins containing data points, then only the centroids associated with those bins should be passed.

ggplot() + 
  geom_hexgrid(
    data = df_bin_centroids, 
    aes(x = c_x, y = c_y)
    ) 
\end{verbatim}

\subsubsection{Triangular mesh}\label{triangular-mesh}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-23-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-31-1}
